Project Setup

### 2024-09-08 choose_license.qmd
Fix typos

First, if you adapt (i.e., modify, build on) a work by others you need to determine if it is provided to you under a free/open license.[You can determine whether a license is free/open by searching for its name in the [SPDX License List](https://spdx.org/licenses/) and looking for at least one `Y` in the two columns _FSF Free/Libre?_ and _OSI Approved?_]{.aside} If yes, we we recommend you to make your contribution available under the same license.^[Copyleft licenses even require you to choose the same or a compatible license.] For example, if you adapt code published in another paper, choose the same license for your modifications. The same applies if there are strong community norms to use a particular free/open license.^[Of course, this is only a heuristic and there might be good reasons to deviate from community norms.] Importantly, as discussed before, you are generally not allowed to adapt a work _not_ published under a free/open license.

>>>>

First, if you adapt (i.e., modify, build on) a work by others you need to determine if it is provided to you under a free/open license.[You can determine whether a license is free/open by searching for its name in the [SPDX License List](https://spdx.org/licenses/) and looking for at least one `Y` in the two columns _FSF Free/Libre?_ and _OSI Approved?_]{.aside} If yes, we recommend you to make your contribution available under the same license.^[Copyleft licenses even require you to choose the same or a compatible license.] For example, if you adapt code published in another paper, choose the same license for your modifications. The same applies if there are strong community norms to use a particular free/open license.^[Of course, this is only a heuristic and there might be good reasons to deviate from community norms.] Importantly, as discussed before, you are generally not allowed to adapt a work _not_ published under a free/open license.

### 2024-09-08 make_readme.qmd
Rename "Add a README" to "Make a README"
Because it fits with the corresponding website:
https://www.makeareadme.com/
Fix typos

---
title: "Add a README"
lang: en
engine: knitr
---

@@

Once you have prepared your project and settled on a license, it is time to add a final touch. Imagine you are coming back to your project in five years, having forgotten most of the details of what you did exactly. What would be useful to know in order to quickly understand what is going on in the project? This is what needs to be described in the README. While you could just start writing along, most READMEs have some sections in common which we describe below.

@@

:   If there is anything you can show that demonstrates how the project can be used? Screenshots or other visuals can make the README more appealing.

@@

:   Is there a recommended way to cite this project? We recommend to increase citability by using the [CodeMeta generator](https://codemeta.github.io/codemeta-generator/) to create the file `codemeta.json`. Alternatively, one can also use the R package [`codemetar`](https://docs.ropensci.org/codemetar/) to create the file.

>>>>

---
title: "Make a README"
lang: en
engine: knitr
---

@@

Once you have prepared your project and settled on a license, it is time to add a final touch. Imagine returning to your project in five years, having forgotten most of the details of what you did exactly. What would be useful to know in order to quickly understand what is going on in the project? This is what needs to be described in the README. While you could just start writing along, most READMEs have some sections in common which we describe below.

@@

:   Is there anything you can show that demonstrates how the project can be used? Screenshots or other visuals can make the README more appealing.

@@

:   Is there a recommended way to cite this project? We recommend to increase citability by using the [CodeMeta generator](https://codemeta.github.io/codemeta-generator/) to create a file called `codemeta.json`. Alternatively, one can also use the R package [`codemetar`](https://docs.ropensci.org/codemetar/) to create this file. Then, put it into the project folder.

### 2024-09-08 setup.qmd
Fix typos

As we will use Git to track the version history of files, be sure to check _Create a git repository_. If you don't know what Git is, have a look at the tutorial "[Introduction to version Control with git and GitHub within RStudio](https://lmu-osc.github.io/Introduction-RStudio-Git-GitHub/)".

@@

Make sure that `.Renviron` is added to your `.gitignore` file in order to exclude it from the Git repository. If you already committed a file that you found contains credentials, you can follow @Chacon2024.
:::

>>>>

As we will use Git to track the version history of files, be sure to check _Create a git repository_. If you don't know what Git is, have a look at the tutorial "[Introduction to version control with git and GitHub within RStudio](https://lmu-osc.github.io/Introduction-RStudio-Git-GitHub/)".

@@

Make sure that `.Renviron` is added to your `.gitignore` file in order to exclude it from the Git repository. If you already committed a file that contains credentials, you can follow @Chacon2024.
:::
